Chapter 4

### 2021-08-06 thesis_chapter_4.Rmd
update to rmd file, age plots included

# Summer
total_summer <- rbind(kom_summer, houtbay_summer, scar_summer, oude_summer, betty_summer, kalk_summer, aframe_summer, sthelena_summer, millers_summer, baboon_summer, basata_summer, buffels_summer, soetwater_summer)

@@

total_autumn <- rbind(kom_autumn, houtbay_autumn, scar_autumn, oude_autumn, betty_autumn, kalk_autumn, aframe_autumn, sthelena_autumn, millers_autumn, baboon_autumn, basata_autumn, buffels_autumn, soetwater_autumn)

@@

total_winter <- rbind(kom_winter, houtbay_winter, scar_winter, oude_winter, betty_winter, kalk_winter, aframe_winter, sthelena_winter, millers_winter, baboon_winter, basata_winter, buffels_winter, soetwater_winter)

@@

total_spring <- rbind(kom_spring, houtbay_spring, scar_spring, oude_spring, betty_spring, kalk_spring, aframe_spring, sthelena_spring, millers_spring, baboon_spring, basata_spring, buffels_spring, soetwater_spring)

@@

>>>>

# Summer
total_summer <- rbind(kom_summer, houtbay_summer, scar_summer, oude_summer, betty_summer, kalk_summer, aframe_summer, sthelena_summer, millers_summer, baboon_summer, basata_summer, buffels_summer, soetwater_summer) 
total_summer$age <- with(total_summer, age/3600)

@@

total_autumn <- rbind(kom_autumn, houtbay_autumn, scar_autumn, oude_autumn, betty_autumn, kalk_autumn, aframe_autumn, sthelena_autumn, millers_autumn, baboon_autumn, basata_autumn, buffels_autumn, soetwater_autumn) 
total_autumn$age <- with(total_autumn, age/3600)

@@

total_winter <- rbind(kom_winter, houtbay_winter, scar_winter, oude_winter, betty_winter, kalk_winter, aframe_winter, sthelena_winter, millers_winter, baboon_winter, basata_winter, buffels_winter, soetwater_winter) 
total_winter$age <- with(total_winter, age/3600)

@@

total_spring <- rbind(kom_spring, houtbay_spring, scar_spring, oude_spring, betty_spring, kalk_spring, aframe_spring, sthelena_spring, millers_spring, baboon_spring, basata_spring, buffels_spring, soetwater_spring) 
total_spring$age <- with(total_spring, age/3600)

@@

```{r message=FALSE, echo=FALSE, warning=FALSE, include=FALSE}

# summer
summer_age <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_summer, aes(x = lon, y = lat, colour = age)) +
  scale_colour_viridis_b(aesthetics = "colour", option = "C", limits = c(0, 1500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Summer") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# autumn
autumn_age <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_autumn, aes(x = lon, y = lat, colour = age)) +
  scale_colour_viridis_b(aesthetics = "colour", option = "C", limits = c(0, 1500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Autumn") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))
# winter
winter_age <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_winter, aes(x = lon, y = lat, colour = age)) +
  scale_colour_viridis_b(aesthetics = "colour", option = "C", limits = c(0, 1300)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Winter") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# spring
spring_age <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_spring, aes(x = lon, y = lat, colour = age)) +
  scale_colour_viridis_b(aesthetics = "colour", option = "C", limits = c(1, 1500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Spring") +
  #theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
```

ggarrange(summer_age, autumn_age, winter_age, spring_age,common.legend = TRUE, font.label = list(size = 12, face = "bold"), legend = c("bottom"), ncol = 2, nrow = 2)
